NumPy---Array Programming in Python

### 2020-01-11 body.tex
Light editing on discussion

Python is already a good choice for many standard programming tasks such as
cleaning data, interacting with web resources and parsing text.
It has a wide range of libraries for many different tasks.
Adding fast array operations and linear algebra allows the scientist to do all
their work with within the same language---and one that has the advantage of
being famously easy to learn and teach.

@@

Lastly, NumPy has benefited greatly from a well-chosen API.
Scientific and numerical programming needs to be fast, and scale to very large
datasets.
The NumPy API defines a simple wrapper for data in memory so it can be
represented as a one- or multi-dimensional array.
The simplicity of this wrapper has made it very successful as a standard way of
representing arrays in memory, and has made it relatively easy for other
libraries to develop fast and memory-efficient compiled code, usually in C or
Fortran, that can manipulate these arrays and pass them back to Python.
This has been a large factor in the growth of numerical computing libraries
around NumPy and Python.

>>>>

Python is already a good choice for many standard programming tasks such as
cleaning data, interacting with web resources, and parsing text.
It has a wide range of libraries for many different tasks.
Adding fast array operations and linear algebra allows the scientist to do all
their work with within the same language---and one that has the advantage of
being famously easy to learn and teach.

@@

Lastly, NumPy benefited greatly from the simplicity of its underlying data structure, which made it a natural standard for exchanging array data between libraries.  It also made it relatively easy for other
libraries to develop fast and memory-efficient compiled code, usually in C or
Fortran, that could manipulate these arrays and pass them back to Python.

Over time, and with the arrival of different technologies and array types, the role of NumPy has changed from merely being an array provider, to being a widely adopted array programming language.
